### 2023-11-27 chapters/discussion.tex
Minor

\todo[inline]{Masked pre-training actually corresponds to marginal maximum likelihood optimization such as done by VAES \parencite{moreno-munoz_masked_2023}. Since maximum likelihood in no way guarantees good representations, how do self"=supervised methods achieve  this, if they also do maximum likelihood?}

>>>>

\todo[inline]{Masked pre-training actually corresponds to marginal maximum likelihood optimization such as done by VAEs \parencite{moreno-munoz_masked_2023}. Since maximum likelihood in no way guarantees good representations, how do self"=supervised methods achieve  this, if they also do maximum likelihood?}
